---
title: "IDEC_Granularity_ManuscriptAnalyses"
author: "Adrienne Bonar"
date:  "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
output:
  html_document:
    toc: yes
    toc_float: yes
---

```{r load-packages}
#Loading packages
library(readxl) #for read_excel
library(readr) #for read_csv
library(magrittr) #for pipes
library(knitr) #for knitting
library(dplyr) #for mutating, filtering data
library(huxtable) #for descriptives table
library(reshape) #for transposing data
library(stringr) #for string manipulations
library(psych) #for descriptives & correlations
library(irr) #for ICCs
library(ggplot2) #for plots
library(nFactors)#for n_factors
library(GPArotation) #for EFA
library(parameters) #for EFA
library(correlation) #for correlations
library(lm.beta) #for regressions
library(apaTables) #for apa style regression tables & comparing models
library(car) #for regression diagnostics
library(imager) #for mediation
library(mediation) #for mediation
library(lavaan) #for SEM/CFA
library(semPlot) #for SEM
```

# Data Prep

```{r data-prep, echo=TRUE}
#Reading in data
DRM_dataset <- readr::read_csv("/Users/adriennebonar/Library/CloudStorage/OneDrive-UniversityofNorthCarolinaatChapelHill/Grad_School/Research/Projects/Granularity/IDEC_Granularity/Data/Granularity_Analyses/datasets/WdataDRM.csv")
IDEC_S1S2_dataset <- readxl::read_excel("/Users/adriennebonar/Library/CloudStorage/OneDrive-UniversityofNorthCarolinaatChapelHill/Grad_School/Research/Projects/Granularity/IDEC_Granularity/Data/Granularity_Analyses/datasets/IDEC_S1S2DataforR_02252020.xlsx") %>%
  dplyr::select(ID, Gender, Race, Age, BMI, PEP_TSSTReactBL, HR_TSSTReactBL, NegHiEmo, NegEmo, HiEmo, 
                PosEmo, LoEmo, contains("PEP"), contains("Emo_"), contains ("SS_"), contains("Sit_")) %>%
  dplyr::mutate(SNSreact = PEP_TSSTReactBL * -1,
                Somatic_mean = (SS_HeartRateIncrease + SS_DiffBreathing + SS_Faint + SS_StomTense + SS_Shaky + SS_Sweaty + 
                                  SS_Pale + SS_StomPit + SS_Red + SS_Butterflies +  SS_Numb + SS_Powerful + SS_Sick + SS_Tense+ 
                                  SS_Sluggish + SS_Empty + SS_Drained+ SS_Exhausted + SS_Headache + SS_Throb + SS_Fidgety + 
                                  SS_Energized + SS_Shivering + SS_SpineTingle + SS_Pain + SS_Stiff + SS_Weak + SS_HeartPound +
                                  SS_Awake + SS_TightChest + SS_Weary + SS_Restless + SS_Jittery + SS_BloodPump+ SS_Cold +
                                  SS_Goosebumps+ SS_Heavy + SS_Hot + SS_HeartPalp + SS_usea+ SS_Tingly + SS_Dizzy)/42)
Qualtrics_S1_dataset <- read_excel("/Users/adriennebonar/Library/CloudStorage/OneDrive-UniversityofNorthCarolinaatChapelHill/Grad_School/Research/Projects/Granularity/IDEC_Granularity/Data/Granularity_Analyses/datasets/IDEC_S1QualHBD_NoDRM_071719.xlsx") %>%
  dplyr::select(ID, contains("RegEff"), contains("RDEES"), contains("Describe"), contains("Identify"), contains("EC")) %>%
  dplyr::mutate(RegEfficacy = (RegEff1 + RegEff2 + RegEff3 + RegEff4)/4,
                Differentiation= (RDEES1 + RDEES2 + RDEES3 + RDEES4 + RDEES5 + RDEES6 + RDEES7)/7,
                Emo_Clarity = ((8- EC7) + (8- EC8_ToReverse) + (8- EC9_ToReverse) + (8-EC10_ToReverse) + (8- EC11_ToReverse) + EC1 + 
                  EC2 + EC3 + EC4 + EC5 + EC6)/11,
                TAS_Describe = ((6- TAS4_Describe_ToReverse) + TAS2_Describe + TAS11_Describe + TAS12_Describe + TAS17_Describe)/6,
                TAS_Identify = (TAS1_Identify + TAS3_Identify + TAS6_Identify + TAS7_Identify + TAS9_Identify + TAS13_Identify +
                                  TAS14_Identify)/7)
Recovery_dataset <- read_excel("/Users/adriennebonar/Library/CloudStorage/OneDrive-UniversityofNorthCarolinaatChapelHill/Grad_School/Research/Projects/Granularity/IDEC_Granularity/Data/Granularity_Analyses/datasets/IDEC_RecoveryScores_01202022.xlsx") %>%
  dplyr::select(ID, PEP_RecoverytoBaseline, RMSDD_RecoverytoBaseline) %>%
  dplyr::mutate(SNSrecover = (PEP_RecoverytoBaseline * -1),
                RMSDDrecover = (RMSDD_RecoverytoBaseline))
RMSDD_dataset <- read_excel("/Users/adriennebonar/Library/CloudStorage/OneDrive-UniversityofNorthCarolinaatChapelHill/Grad_School/Research/Projects/Granularity/IDEC_Granularity/Data/Granularity_Analyses/datasets/IDEC_S2_RMSDDs_08202021.xlsx") %>%
  dplyr::select(ID, cvRMSDD_TSSTReact, RMSDD_TSSTReact)

#Merge into one dataframe
noicc_dataset <- merge(Qualtrics_S1_dataset, IDEC_S1S2_dataset, by=("ID"))
noicc_dataset <- merge(noicc_dataset, Recovery_dataset, by=("ID"))
noicc_dataset <- merge(noicc_dataset,RMSDD_dataset, by=("ID"))

#Demographic variables as factors
noicc_dataset$Race <- factor(noicc_dataset$Race, levels = c(1,2,3,4,5,6,7,8), labels = c("American Indian or Alaskan Native", "Asian American", "Native Hawaiian or other Pacific Islander", "African American", "European American", "Latin American","More than one race", "Other")) #labeling race
noicc_dataset$Sex <- factor(noicc_dataset$Gender, levels = c(0,1), labels = c("Female", "Male")) #labeling sex
```

## ICCs for trait emo granularity

```{r granularity, echo=TRUE}
#code adapted from Kalokerinos, E. K., Erbas, Y., Ceulemans, E., & Kuppens, P. (2019). Differentiate to regulate: Low negative emotion differentiation is associated with ineffective use but not selection of emotion-regulation strategies. Psychological Science, 30(6), 863-879. https://osf.io/bmaf2/

subjects_neg=unique(DRM_dataset$ID)

#Trait ICCs for NEGATIVE emotion 
icc_list_neg=NULL #creating empty dataframe
for (sub in subjects_neg){
  sub_ldata_neg=DRM_dataset[DRM_dataset[,2]==sub,c("Anger", "Anxious", "Boredom", "Bittersweet", "Disgust", "Embarrass", "Fear", "Guilt", "Irritable", "Jealous", "Sad")]  #selecting data for current subject
  icc=icc(sub_ldata_neg, model="twoway",type = "agreement", unit="average")  #computes ICC
  icc_temp=icc$value

  icc_temp[icc_temp < 0] <- 0 #transforming negative ICC values to 0 per recommendations in Cohen et al. (2003); 37 subjects' ICC values were transformed 
  
  fz_iccTemp=fisherz(icc_temp) #fisher z transformation
  row_temp=c(sub,icc_temp, fz_iccTemp) #creating temporary matrix for current subject with ID, ICC, and fisher transformed ICC
  icc_list_neg=rbind(icc_list_neg,row_temp)
}

icc_list_neg=as.data.frame(icc_list_neg)
colnames(icc_list_neg)=c("ID","ICCneg", "ICCneg_fz")

icc_list_neg_complete=icc_list_neg[complete.cases(icc_list_neg),]  #choosing subjects with both ICC and fisher transformed ICC

#Trait ICCs for POSITIVE emotion
subjects_pos=unique(DRM_dataset$ID)

icc_list_pos=NULL #creating empty dataframe
for (sub in subjects_pos){
  sub_ldata_pos=DRM_dataset[DRM_dataset[,2]==sub,c("Amusement", "Awe", "Content", "Excitement", "Gratitude", "Happy", "Love", "Pleased", "Proud")]  #selecting data for current subject
  
  icc_p=icc(sub_ldata_pos, model="twoway",type= "agreement", unit="average")  #computes ICC
  icc_p_temp=icc_p$value
  
  icc_p_temp[icc_p_temp <0] <- 0 #transforming negative ICC values to 0 per recommendations in Cohen et al. (2003); 3 subjects ICC values were transformed
  
  fz_p_iccTemp=fisherz(icc_p_temp) #fisher z transformation
  
  row_p_temp=c(sub,icc_p_temp, fz_p_iccTemp) #creating temporary matrix for current subject with ID, ICC, and fisher transformed ICC
  icc_list_pos=rbind(icc_list_pos,row_p_temp)
}

icc_list_pos=as.data.frame(icc_list_pos) 
colnames(icc_list_pos)=c("ID","ICCpos", "ICCpos_fz") #renaming columns

icc_list_pos_complete=icc_list_pos[complete.cases(icc_list_pos),]  #choosing subjects with both ICC and fisher transformed ICC

#Merging ICC dataframes together
icc_dataset <- merge(icc_list_neg, icc_list_pos,  by=c("ID"))

#Reverse scoring the ICC so higher ICC = higher granularity
icc_dataset$ICCneg_fz_rev <- -1* icc_dataset$ICCneg_fz
icc_dataset$ICCpos_fz_rev <- -1* icc_dataset$ICCpos_fz
```

## Person-level mean negative and positive emotion

```{r mean-emotionality}
subjects_DRM=unique(DRM_dataset$ID)

DRM_mean=NULL #creating empty dataframe
for (sub in subjects_DRM){
  DRM_ldata=DRM_dataset[DRM_dataset[,2]==sub,c("Anger", "Anxious", "Boredom", "Bittersweet", "Disgust", "Embarrass", "Fear", "Guilt", "Irritable", "Jealous", "Sad", "Amusement", "Awe", "Content", "Excitement", "Gratitude", "Happy", "Love", "Pleased", "Proud")]  #selecting all data for current subject
  
#Computing mean negative emotion
mean_neg= rowMeans(subset(DRM_ldata, select=c("Anger", "Anxious", "Boredom", "Bittersweet", "Disgust", "Embarrass", "Fear", "Guilt", "Irritable", "Jealous", "Sad")), na.rm=TRUE)
temp_mean_neg = mean(mean_neg, na.rm=TRUE)

#Computing mean positive emotion
mean_pos <- rowMeans(subset(DRM_ldata, select=c("Amusement", "Awe", "Content", "Excitement", "Gratitude", "Happy", "Love", "Pleased", "Proud")), na.rm=TRUE)
temp_mean_pos= mean(mean_pos, na.rm= TRUE)

row_temp = c(sub, temp_mean_neg, temp_mean_pos)
DRM_mean=rbind(DRM_mean, row_temp)
}

colnames(DRM_mean)=c("ID","DRMneg_mean","DRMpos_mean") #renaming columns
DRM_mean= as.data.frame(DRM_mean)

icc_dataset <- merge(DRM_mean, icc_dataset, by = c("ID")) #merging emotion mean data with ICC data

#Merging ICCs into main dataset
data <- merge(noicc_dataset, icc_dataset, by= c("ID"))
data <- as.data.frame(data)
```

## Emo complexity EFA (using subscale scores)

```{r, efa-complexity-describe}
efa_means_dataset <- data %>%
  dplyr::select(ID, ICCneg_fz_rev, ICCpos_fz_rev, Differentiation, Emo_Clarity, TAS_Describe, TAS_Identify)

psych::describe(efa_means_dataset[2:length(efa_means_dataset)], fast = FALSE)
psych::multi.hist(efa_means_dataset[2:length(efa_means_dataset)]) #printing histograms to check the distribution of responses per item
lowerCor(efa_means_dataset[2:length(efa_means_dataset)], digits=2) #looking at bivariate correlations among items
```

### Scree plot

```{r, efa-complexity-enumeration}
#Checking suitability of data for Factor Analysis
parameters::check_factorstructure(efa_means_dataset[2:length(efa_means_dataset)])

#Checking for number of factors
factors <- n_factors(efa_means_dataset[2:length(efa_means_dataset)])
psych::scree(efa_means_dataset[2:length(efa_means_dataset)], factors = T) #generating a scree.plot of the eigenvalues

#Running parallel analysis
parallel <- fa.parallel(efa_means_dataset[2:length(efa_means_dataset)], fa='pc') 

#Creating a data frame from observed eigenvalues in 'parallel'
eigen <- data.frame(parallel$fa.values)
eigen$num <- c(row.names(eigen))
eigen$num <- as.numeric(eigen$num)
colnames(eigen) <-c('eigenvalue', 'factor number')

```

### EFA Results

```{r, efa-complexity-extraction}
#Performing EFA with 1 factor using maximum likelihood with promax rotation 
fa1 <- fa(efa_means_dataset[2:length(efa_means_dataset)], nfactors= 1, rotate= 'promax', fm='ml', scores = "regression")
print(fa1) #fit indices suggest okay model fit

#Running same model but dropping ICCpos and ICCneg
fa2 <- fa(efa_means_dataset[2:length(efa_means_dataset)] %>% dplyr::select(-contains("ICC")), nfactors= 1, rotate= 'promax', fm='ml', scores = "regression")
print(fa2) #fit indices are worse

#Getting factor scores
fs <- fa1$scores 
full_efa_dataset <- cbind(fs, efa_means_dataset[1])

#Merge EFA data with the rest of the data
data <- merge(full_efa_dataset, data, by=c("ID"))
```


## Post-TSST appraisals EFA

```{r efa-appraise-describe}
judgement_dataset <- data %>%
  dplyr::select(ID, contains("Sit_")) %>%
  tidyr::drop_na()

psych::describe(judgement_dataset[2:26], fast = FALSE) 
psych::multi.hist(judgement_dataset[2:26]) #printing histograms to check the distribution of responses per item; several items aren't normally distributed

```

### Scree Plot

```{r efa-appraise-enumeration}
#Checking suitability of data for EFA
parameters::check_factorstructure(judgement_dataset[2:26])

#Checking for number of factors
factors <- n_factors(judgement_dataset[2:26])
psych::scree(judgement_dataset[2:26], factors = T) #generating a scree.plot of the eigenvalues

#Running parallel analysis
parallel <- fa.parallel((judgement_dataset[2:26]), fa='pc') 

#Creating a data frame from observed eigenvalues in 'parallel'
eigen <- data.frame(parallel$fa.values)
eigen$num <- c(row.names(eigen))
eigen$num <- as.numeric(eigen$num)
colnames(eigen) <-c('eigenvalue', 'factor number')

```

### EFA/CFA Results

```{r efa-appraise-extraction}
#Performing EFA with 2 factors using weighted least squares 
fa3 <- psych::fa(judgement_dataset[2:26], nfactors = 2, rotate = "promax", fm= "wls")
print(fa3) 

judgement_dataset_temp <- judgement_dataset %>%
  dplyr::select(-(Sit_BadNews), -(Sit_Loss), -(Sit_Disgraced))

#Re-running EFA with 2 factors using maximum likelihood vs. weighted least squares 
fa4 <- psych::fa(judgement_dataset_temp[2:23], nfactors = 2, rotate = "promax", fm= "ml") 
print(fa4) 

fa4a <- psych::fa(judgement_dataset_temp[2:23], nfactors = 2, rotate = "promax", fm= "wls", scores = "regression")
print(fa4a) 

#Getting factor scores
fs2 <- fa4a$scores 
full_judgement_dataset <- cbind(fs2, judgement_dataset[1])

#Merge EFA data with the rest of the data
data <- merge(full_judgement_dataset, data, by=c("ID"))
```

# Descriptives

## Exclusions

```{r missing-data}
exclusion_data <- data %>%
  dplyr::select(ID, Age, Sex, Race, BMI, DRMneg_mean, DRMpos_mean, DRMpos_mean, ICCneg_fz_rev, ICCpos_fz_rev, ML1, Emo_Clarity, Differentiation, TAS_Describe, TAS_Identify, RegEfficacy, SNSreact, SNSrecover, RMSDDrecover, RMSDD_TSSTReact, cvRMSDD_TSSTReact, HR_TSSTReactBL, NegHiEmo, HiEmo, PosEmo, Somatic_mean, contains("Sit_"), contains("Emo"), contains("SS"), WLS1, WLS2)

exclusion_data$Complexity <- exclusion_data$ML1 #renaming complexity factor score column
exclusion_data$OtherBlame <- exclusion_data$WLS1 #renaming complexity factor score column
exclusion_data$SelfBlame <- exclusion_data$WLS2 #renaming complexity factor score column

df_exclusions_ICCneg <- exclusion_data %>%
  dplyr::filter(is.na(ICCneg_fz_rev == T))
nrow(df_exclusions_ICCneg) #0 subjects missing ICC neg data

df_exclusions_ICCpos <- exclusion_data %>%
  filter(is.na(ICCpos_fz_rev == T))
nrow(df_exclusions_ICCpos) #0 subjects missing ICC pos data

df_exclusions_BMI <- exclusion_data %>%
  filter(is.na(BMI == T))
nrow(df_exclusions_BMI) #ID 24 doesn't have BMI info

df_exclusions_SNS <- exclusion_data %>%
  filter(is.na(SNSreact == T))
nrow(df_exclusions_SNS) #50 subject missing PEP data - 21 subjects due to technical difficulties or poor quality data, 27 didn't complete S2, ID 24 doesn't have BMI info, 1 subject data missing

#Creating final data set
final_data <- exclusion_data %>%
  dplyr::select(ID, Age, Sex, Race, BMI, DRMneg_mean, DRMpos_mean, DRMpos_mean, ICCneg_fz_rev, ICCpos_fz_rev, Complexity, RegEfficacy, SNSreact, SNSrecover, RMSDDrecover, RMSDD_TSSTReact, cvRMSDD_TSSTReact, HR_TSSTReactBL, NegHiEmo, HiEmo, PosEmo, Somatic_mean, OtherBlame, SelfBlame) %>%
  tidyr::drop_na()
```


## Frequency of participants by race and sex

```{r categorical-freq}
summary(final_data$Race) #frequency by race 
summary(final_data$Sex) #frequency of females and males
```

## Descriptives for variables of interest

```{r descriptives}
df_descriptives <- final_data %>%
  dplyr::select("Age", "BMI", "DRMneg_mean", "DRMpos_mean", "ICCneg_fz_rev", "ICCpos_fz_rev", "Complexity", "OtherBlame", "SelfBlame", "RegEfficacy","SNSrecover", "RMSDDrecover", "RMSDD_TSSTReact", "cvRMSDD_TSSTReact", "SNSreact", "HR_TSSTReactBL","NegHiEmo", "Somatic_mean", "HiEmo")

descriptives <- psych::describe(df_descriptives, skew = T, ranges = T)
print(descriptives)

#Printing histogram for continuous variables
psych::multi.hist(df_descriptives, global = F) #Somatic_mean & OtherBlame are positively skewed

df_descriptives <- df_descriptives %>%
  dplyr::mutate(logOtherBlame = log10(OtherBlame + 1), #log-transforming to account for skew
                logSomatic_mean  = log10(Somatic_mean + 1))

psych::multi.hist(df_descriptives, global = F) #distribution looks more normal

#Adding log-transformed variables to final dataset
final_data <- final_data %>%
  dplyr::mutate(logOtherBlame = log10(OtherBlame+ 1), 
                logSomatic_mean  = log10(Somatic_mean + 1))
```

## Reliability

```{r alphas}
#Reliability for TAS20 Describe
TASDescribe_alpha <- data %>%
  dplyr::select(ID, contains("Describe")) 
TASDescribe_alpha$TAS4_Describe = 6 - TASDescribe_alpha$TAS4_Describe_ToReverse #reverse scoring relevant items

TASDescribe_alpha_calc <-psych::alpha(TASDescribe_alpha[,c("TAS2_Describe", "TAS11_Describe", "TAS12_Describe", "TAS17_Describe", "TAS4_Describe")], #computing reliability
                                  keys = NULL, cumulative = F, 
                                  na.rm = T, check.keys= F, delete = F, 
                                  use = "pairwise")
TASDescribe_alpha_summary <- TASDescribe_alpha_calc$total

final_data$TASDescribe_alpha_raw <- TASDescribe_alpha_summary$raw_alpha #storing raw alpha in main dataset
final_data$TASDescribe_alpha_std <- TASDescribe_alpha_summary$std.alpha #storing standard alpha in main dataset

#Reliability for TAS20 Identify
TASIdentify_alpha <- data %>%
  dplyr::select(ID, contains("Identify"))

TASIdentify_alpha_calc <-psych::alpha(TASIdentify_alpha[2:length(TASIdentify_alpha)], #computing reliability
                                  keys = NULL, cumulative = F, 
                                  na.rm = T, check.keys= F, delete = F, 
                                  use = "pairwise")
TASIdentify_alpha_summary <- TASIdentify_alpha_calc$total

final_data$TASIdentify_alpha_raw <- TASIdentify_alpha_summary$raw_alpha #storing raw alpha in main dataset
final_data$TASIdentify_alpha_std <- TASIdentify_alpha_summary$std.alpha #storing standard alpha in main dataset

#Reliability for RDEES
RDEES_alpha <- data %>%
  dplyr::select(ID, RDEES1, RDEES2, RDEES3, RDEES4, RDEES5, RDEES6, RDEES7)

RDEES_alpha_calc <-psych::alpha(RDEES_alpha[2:length(RDEES_alpha)], #computing reliability
                                  keys = NULL, cumulative = F, 
                                  na.rm = T, check.keys= F, delete = F, 
                                  use = "pairwise")
RDEES_alpha_summary <- RDEES_alpha_calc$total

final_data$RDEES_alpha_raw <- RDEES_alpha_summary$raw_alpha #storing rawalpha in main dataset
final_data$RDEES_alpha_std <- RDEES_alpha_summary$std.alpha #storing standard alpha in main dataset

#Reliability for Emo_Clarity
Emo_Clarity_alpha <- data %>%
  dplyr::select(ID, EC1, EC2, EC3, EC4, EC5, EC6, EC7, EC8_ToReverse, EC9_ToReverse, EC10_ToReverse, EC11_ToReverse)

Emo_Clarity_alpha_calc <-psych::alpha(Emo_Clarity_alpha[2:length(Emo_Clarity_alpha)], #computing reliability
                                  keys = NULL, cumulative = F, 
                                  na.rm = T, check.keys= T, delete = F, 
                                  use = "pairwise")

Emo_Clarity_alpha_summary <- Emo_Clarity_alpha_calc$total

final_data$Emo_Clarity_alpha_raw <- Emo_Clarity_alpha_summary$raw_alpha #storing rawalpha in main dataset
final_data$Emo_Clarity_alpha_std <- Emo_Clarity_alpha_summary$std.alpha #storing standard alpha in main dataset

#Regulatory self-efficacy
RegEff_alpha <- data %>%
  dplyr::select(ID, RegEff1, RegEff2, RegEff3, RegEff4)

RegEff_alpha_calc <- psych::alpha(RegEff_alpha[2:length(RegEff_alpha)], #computing relability
                                    keys = NULL, cumulative = F, 
                                  na.rm = T, check.keys= F, delete = F, 
                                  use = "pairwise")

RegEff_alpha_summary <- RegEff_alpha_calc$total
final_data$RegEff_alpha_raw <- RegEff_alpha_summary$raw_alpha #storing rawalpha in main dataset
final_data$RegEff_alpha_std <- RegEff_alpha_summary$std.alpha #storing standard alpha in main dataset

#Negative high arousal emotion
NegHiEmo_alpha <- data %>%
  dplyr::select(ID, Emo_Activated, Emo_Afraid, Emo_Alert, Emo_Angry, Emo_Annoyed, Emo_Anxious, Emo_Disgusted, Emo_Distressed, Emo_Embarrassed, Emo_Frustrated, Emo_Guilty, Emo_Hyperactive, Emo_Irritiable, Emo_Panicky, Emo_Stressed)

NegHiEmo_alpha_calc <- psych::alpha(NegHiEmo_alpha[2:length(NegHiEmo_alpha)], #computing relbiality
                                    keys = NULL, cumulative = F, 
                                  na.rm = T, check.keys= F, delete = F, 
                                  use = "pairwise")

NegHiEmo_alpha_summary <- NegHiEmo_alpha_calc$total
final_data$NegHiEmo_alpha_raw <- NegHiEmo_alpha_summary$raw_alpha #storing rawalpha in main dataset
final_data$NegHiEmo_alpha_std <- NegHiEmo_alpha_summary$std.alpha #storing standard alpha in main dataset

SS_data <- data%>%
  dplyr::select(ID, contains("SS_"), -HBD_miss_count)

SS_alpha_calc <- psych::alpha(SS_data[2:length(SS_data)], keys= T, cumulative=F, na.rm=T, check.keys = F, delete=F, use="pairwise")

SS_alpha_summary <- SS_alpha_calc$total
final_data$SS_alpha_raw <-SS_alpha_summary$raw_alpha
final_data$SS_alpha_std <-SS_alpha_summary$std.alpha
```

# Bivariate correlations between variables of interest

```{r correlations}
corr_small<- final_data %>%
  dplyr::select("FactorScore", "DRMneg_mean", "DRMpos_mean", "ICCneg_fz_rev", "ICCpos_fz_rev", "SNSreact", "NegHiEmo")

apaTables::apa.cor.table(corr_small, table.number = NA, show.conf.interval = FALSE, show.sig.stars = TRUE, landscape = FALSE)
```

# Hierachical regressions analyses for main manuscript

```{r regression-prep}
#Centering predictors and standardizing interaction terms
final_data <- final_data %>%
  dplyr::mutate(Age_c = scale(Age, center = T, scale = F),
                BMI_c = scale(BMI, center = T, scale = F),
                DRMneg_mean_c = scale(DRMneg_mean, center = T, scale =F),
                DRMpos_mean_c = scale(DRMneg_mean, center = T, scale=F),
                FactorScore_c = scale(FactorScore, center = T, scale = F),
                RegEfficacy_z = scale(RegEfficacy, center =T, scale =T),
                Threat_mean_z = scale(Threat_mean, center = F, scale = T),
                Challenged_mean_z = scale(Challenged_mean, center = F, scale = T),
                SNSreact_z = scale(SNSreact, center = F, scale = T),
                SNSrecover_z = scale(SNSrecover, center = F, scale =T),
                RMSDDreact_z = scale(cvRMSDD_TSSTReact, center = F, scale = T),
                RMSDDrecover_z = scale(RMSDDrecover, center= F, scale = T))
```


```{r diagnositc-func}
#Making function for diagnostics; function adapted from Feldman, M.J., MacCormack, J.K., Bonar, A.S., and Lindquist, K.A. (2021). Interoceptive ability moderates the effect of physiological reactivity on social judgment https://osf.io/8ys5a/

model_diagnose_params <- function(mod, n, Data){
  model_params <- as.data.frame(matrix(nrow = n, ncol = 1))
  model_params$V1 <- Data[["ID"]]
  model_params$Res <- mod[["residuals"]]
  model_params$Pred <- mod[["fitted.values"]]  
  model_params$StudDelRes <- rstudent(mod)
  model_params$StanDelRes <- rstandard(mod)
  model_params$HatVals <- hatvalues(mod)
  model_params$Cooks <- cooks.distance(mod)
  model_params$DFFITS <- dffits(mod)
  

  print("checking for multicollinearity (with caution due to interaction terms). 
        Look for values >5 and >10.")
  print(vif(mod))
  
  print("Evaluating the assumption that the unique effect of each predictor on the outcome is linear")
  avPlots(mod, grid=T, main = "Partial Regression Plots")
  qqPlot(mod, main = "QQ Plot")
  print("Evaluating the assumptions of normality and homoscedasticity (constant variance) 
        for the residuals")
  print("check to see whether datapoints are distributed evenly above and below the mean 
        and across th horizontal axis (no funnel)")
  print(ggplot(data = model_params, aes(x = Pred, y = Res)) +
  geom_point() + geom_hline(yintercept = 0, linetype = "dashed") + 
  xlab("predicted values") + ylab("residuals") +
  labs(title = "Residuals ~ Fitted values") +
  theme(plot.title = element_text(hjust = 0.5)))
  
  print("Identifying any cases with residuals that are large enough to be of 
        potential concern, > |3|")
  print(model_params[which(abs(model_params$StudDelRes) > 3),])
  
  residPLOT <- ggplot(data = model_params, 
                      mapping = aes(x = V1, y = abs(StudDelRes))) + geom_point() +
    geom_segment(aes (x = V1, y = 0, xend = V1, yend = abs(StudDelRes))) + 
    geom_hline(yintercept = 3, color = "red", linetype = "dashed") + 
    labs(title = "Large Residuals?") + xlab(NULL)
  
  print("Identify any cases with moderately concerning leverage, > 0.2 and < 0.5")
  print(model_params[which(model_params$HatVals > 0.2 & model_params$HatVals < 0.5),] )
  print("Identify any cases with very concerning leverage, > 0.5")
  print(model_params[which(model_params$HatVals > 0.5),])
  
  
  LevPlot <- ggplot(data = model_params, mapping = aes(x = V1, y = HatVals)) + 
    geom_point() + geom_segment(aes (x = V1, y = 0, xend = V1, yend = HatVals)) + 
    geom_hline(yintercept = 0.2, color = "orange", linetype = "dashed") +
    geom_hline(yintercept = 0.5, color = "red", linetype = "dashed") + 
    labs(title = "High Leverage?") + xlab(NULL)
  
  print("Determining if any cases may be having undue influence on results, 
  both with respect to the entire model and with respect to specific
  regression coefficient estimates.")
  cutoff <- qf(.1, 7, (nrow(model_params)-7), lower.tail = T) 
  print((model_params[which(model_params$Cooks > cutoff),] ))
  
  
  InfPlot <- ggplot(data = model_params, mapping = aes(x = V1, y = Cooks)) + 
    geom_point() + geom_segment(aes (x = V1, y = 0, xend = V1, yend = Cooks)) + 
    geom_hline(yintercept = cutoff, color = "red", linetype = "dashed") + 
    labs(title = "High Influence?") + xlab(NULL)
  
  print(ggpubr::ggarrange(residPLOT, LevPlot, InfPlot, nrow = 3))
  
  print("lm function for plotting cooks distance")
  plot(mod, which = 5)
}

```

## MODERATIONS: Granularity and physio reactivity predicting rating intensity

### Regressions for Model 1a: Granularity and SNS reactivity on NegHi emotion

```{r reg-1a}
#Regressions for Model 1a: Negative granularity and SNS reactivity on NegHi emotion
NegHiMod1.1 <- lm(formula = NegHiEmo ~ ICCneg_fz_rev, data= final_data)
NegHiMod1.2 <- lm(formula = NegHiEmo ~ ICCneg_fz_rev + SNSreact_z, data= final_data)
NegHiMod1.3 <- lm(formula = NegHiEmo ~ ICCneg_fz_rev * SNSreact_z, data= final_data) 
NegHiMod1.4 <- lm(formula = NegHiEmo ~ ICCneg_fz_rev * SNSreact_z + FactorScore + Sex + Age_c + BMI_c + DRMneg_mean_c, data= final_data)
NegHiMod1.5 <- lm(formula = NegHiEmo ~ ICCneg_fz_rev + SNSreact_z + FactorScore + Sex + Age_c + BMI_c + DRMneg_mean_c, data= final_data)

summary(NegHiMod1.1) #results summaries
summary(NegHiMod1.2)
summary(NegHiMod1.3)
summary(NegHiMod1.4)
summary(NegHiMod1.5)

table3a <- apa.reg.table(NegHiMod1.1, NegHiMod1.2, NegHiMod1.3, NegHiMod1.4, filename = "/Users/adriennebonar/Desktop/datasets/table3a.doc", table.number = 3)$table_body #model comparison table

```

```{r reg-1a-pos} 
#Regressions for Positive granularity and SNS reactivity on NegHi emotion
NegHiMod1.5 <- lm(formula = NegHiEmo ~ ICCpos_fz_rev, data= final_data)
NegHiMod1.6 <- lm(formula = NegHiEmo ~ ICCpos_fz_rev + SNSreact_z, data= final_data)
NegHiMod1.7 <- lm(formula = NegHiEmo ~ ICCpos_fz_rev * SNSreact_z, data= final_data) 
NegHiMod1.8 <- lm(formula = NegHiEmo ~ ICCpos_fz_rev * SNSreact_z + FactorScore + Sex + Age_c + BMI_c + DRMpos_mean_c, data= final_data)
NegHiMod1.9 <- lm(formula = NegHiEmo ~ ICCpos_fz_rev + SNSreact_z + FactorScore + Sex + Age_c + BMI_c + DRMpos_mean_c, data= final_data)

summary(NegHiMod1.5) #results summaries
summary(NegHiMod1.6)
summary(NegHiMod1.7)
summary(NegHiMod1.8)
summary(NegHiMod1.9)

table3b <- apa.reg.table(NegHiMod1.5, NegHiMod1.6, NegHiMod1.7, NegHiMod1.8, filename = "/Users/adriennebonar/Desktop/datasets/table3b.doc", table.number = 4)$table_body #model comparison table
```

#### Model Diagnostics

```{r model1a-pos-diagnositc}
model_diagnose_params(NegHiMod1.8, 180, final_data)
```

### Regressions for Model 1b: Granularity and SNS reactivity on somatic intensity

```{r reg-1b}
#Regressions for Model 1b: Negative granularity and SNS reactivity on somatic intensity rating mean
SomMod1.1 <- lm(formula = logSomatic_mean ~ ICCneg_fz_rev, data= final_data)
SomMod1.2 <- lm(formula = logSomatic_mean ~ ICCneg_fz_rev + SNSreact_z, data= final_data)
SomMod1.3 <- lm(formula = logSomatic_mean ~ ICCneg_fz_rev * SNSreact_z, data= final_data) 
SomMod1.4 <- lm(formula = logSomatic_mean ~ ICCneg_fz_rev * SNSreact_z + FactorScore + Age_c + Sex + BMI_c + DRMneg_mean_c, data= final_data)

summary(SomMod1.1) #results summaries
summary(SomMod1.2)
summary(SomMod1.3)
summary(SomMod1.4)

table4a <- apa.reg.table(SomMod1.1, SomMod1.2, SomMod1.3, SomMod1.4, filename = "/Users/adriennebonar/Desktop/datasets/table4a.doc", table.number = 4)$table_body #model comparison table
```

#### Model Diagnostics

```{r model1b-diagnositc}
model_diagnose_params(SomMod1.4, 180, final_data) #consider running model with IDs 186, 86, 118, and 160 removed
```


```{r reg-1b-pos}
#Positive granularity and SNS reactivity on somatic intensity rating mean
SomMod1.5 <- lm(formula = logSomatic_mean ~ ICCpos_fz_rev, data= final_data)
SomMod1.6 <- lm(formula = logSomatic_mean ~ ICCpos_fz_rev + SNSreact_z, data= final_data)
SomMod1.7 <- lm(formula = logSomatic_mean ~ ICCpos_fz_rev * SNSreact_z, data= final_data) 
SomMod1.8 <- lm(formula = logSomatic_mean ~ ICCpos_fz_rev * SNSreact_z + FactorScore + Age_c + Sex + BMI_c + DRMpos_mean_c, data= final_data)

summary(SomMod1.5) #results summaries
summary(SomMod1.6)
summary(SomMod1.7)
summary(SomMod1.8)

apa.reg.table(SomMod1.5, SomMod1.6, SomMod1.7, SomMod1.8)$table_body #model comparison table
table4b <- apa.reg.table(SomMod1.5, SomMod1.6, SomMod1.7, SomMod1.8, filename = "/Users/adriennebonar/Desktop/datasets/table4b.doc", table.number = 4)$table_body #model comparison table
```

#### Model Diagnostics

```{r model1b-pos-diagnositc}
model_diagnose_params(SomMod1.8, 180, final_data) 
```

### Regressions for Model 1c: Granularity and SNS reactivity on Other-focused Neg Appraisals

```{r reg-1c}
#Regressions for Model 1d: Negative granularity and SNS reactivity on other appraisals - normal GLM
OtherMod1.1 <- lm(formula = Other ~ ICCneg_fz_rev, data= final_data)
OtherMod1.2 <- lm(formula = Other ~ ICCneg_fz_rev + SNSreact_z, data= final_data)
OtherMod1.3 <- lm(formula = Other ~ ICCneg_fz_rev * SNSreact_z, data= final_data) 
OtherMod1.4 <- lm(formula = Other ~ ICCneg_fz_rev * SNSreact_z + FactorScore + Age_c + Sex + BMI_c + DRMneg_mean_c, data= final_data)

summary(OtherMod1.1) #results summaries
summary(OtherMod1.2)
summary(OtherMod1.3)
summary(OtherMod1.4)

apa.reg.table(OtherMod1.1, OtherMod1.2, OtherMod1.3, OtherMod1.4)$table_body #model comparison table
```


```{r}
#Positive granularity and SNS reactivity on other appraisals - normal GLM
OtherMod1.5 <- lm(formula = Other ~ ICCpos_fz_rev, data= final_data)
OtherMod1.6 <- lm(formula = Other ~ ICCpos_fz_rev + SNSreact_z, data= final_data)
OtherMod1.7 <- lm(formula = Other ~ ICCpos_fz_rev * SNSreact_z, data= final_data) 
OtherMod1.8 <- lm(formula = Other ~ ICCpos_fz_rev * SNSreact_z + FactorScore + Age_c + Sex + BMI_c + DRMpos_mean_c, data= final_data)

summary(OtherMod1.5) #results summaries
summary(OtherMod1.6)
summary(OtherMod1.7)
summary(OtherMod1.8)

apa.reg.table(OtherMod1.5, OtherMod1.6, OtherMod1.7, OtherMod1.8)$table_body #model comparison table
```

### Regressions for Model 1d: Granularity and SNS reactivity on Self-focused Neg Appraisals

```{r reg-1d}
#Regressions for Model 1d: Negative granularity and SNS reactivity on self appraisals
SelfMod1.1 <- lm(formula = Self ~ ICCneg_fz_rev, data= final_data)
SelfMod1.2 <- lm(formula = Self ~ ICCneg_fz_rev + SNSreact_z, data= final_data)
SelfMod1.3 <- lm(formula = Self ~ ICCneg_fz_rev * SNSreact_z, data= final_data) 
SelfMod1.4 <- lm(formula = Self ~ ICCneg_fz_rev * SNSreact_z + FactorScore + Age_c + Sex + BMI_c + DRMneg_mean_c, data= final_data)

summary(SelfMod1.1) #results summaries
summary(SelfMod1.2)
summary(SelfMod1.3)
summary(SelfMod1.4)

apa.reg.table(SelfMod1.1, SelfMod1.2, SelfMod1.3, SelfMod1.4)$table_body #model comparison table
```

```{r}
#Positive granularity and SNS reactivity on self appraisals
SelfMod1.5 <- lm(formula = Self ~ ICCpos_fz_rev, data= final_data)
SelfMod1.6 <- lm(formula = Self ~ ICCpos_fz_rev + SNSreact_z, data= final_data)
SelfMod1.7 <- lm(formula = Self ~ ICCpos_fz_rev * SNSreact_z, data= final_data) 
SelfMod1.8 <- lm(formula = Self ~ ICCpos_fz_rev * SNSreact_z + FactorScore + Age_c + Sex + BMI_c + DRMpos_mean_c, data= final_data)

summary(SelfMod1.5) #results summaries
summary(SelfMod1.6)
summary(SelfMod1.7)
summary(SelfMod1.8)

apa.reg.table(SelfMod1.5, SelfMod1.6, SelfMod1.7, SelfMod1.8)$table_body #model comparison table
```

### Regressions for Model 2a: Granularity and HRV reactivity on NegHi emotion

```{r reg-2a}
#Regressions for Model 2a: Negative granularity and corrected HRV reactivity on NegHi emotion
NegHiMod2.1 <- lm(formula = NegHiEmo ~ ICCneg_fz_rev, data= final_data)
NegHiMod2.2 <- lm(formula = NegHiEmo ~ ICCneg_fz_rev + RMSDDreact_z, data= final_data)
NegHiMod2.3 <- lm(formula = NegHiEmo ~ ICCneg_fz_rev * RMSDDreact_z, data= final_data) 
NegHiMod2.4 <- lm(formula = NegHiEmo ~ ICCneg_fz_rev * RMSDDreact_z + FactorScore + Sex + BMI_c + DRMneg_mean_c, data= final_data)

summary(NegHiMod2.1) #results summaries
summary(NegHiMod2.2)
summary(NegHiMod2.3)
summary(NegHiMod2.4)

apa.reg.table(NegHiMod2.1, NegHiMod2.2, NegHiMod2.3, NegHiMod2.4)$table_body #model comparison table
```


```{r reg-2a-pos}
#Positive granularity and corrected HRV reactivity on NegHi emotion
NegHiMod2.5 <- lm(formula = NegHiEmo ~ ICCpos_fz_rev, data= final_data)
NegHiMod2.6 <- lm(formula = NegHiEmo ~ ICCpos_fz_rev + RMSDDreact_z, data= final_data)
NegHiMod2.7 <- lm(formula = NegHiEmo ~ ICCpos_fz_rev * RMSDDreact_z, data= final_data) 
NegHiMod2.8 <- lm(formula = NegHiEmo ~ ICCpos_fz_rev * RMSDDreact_z + FactorScore + Sex + BMI_c + DRMpos_mean_c, data= final_data)

summary(NegHiMod2.5) #results summaries
summary(NegHiMod2.6)
summary(NegHiMod2.7)
summary(NegHiMod2.8)

apa.reg.table(NegHiMod2.5, NegHiMod2.6, NegHiMod2.7, NegHiMod2.8)$table_body #model comparison table
```


### Regressions for Model 2b: Granularity and HRV reactivity on somatic intensity

```{r reg-2b}
#Regressions for Model 2b: Negative granularity and corrected HRV reactivity on somatic intensity
SomMod2.1 <- lm(formula = logSomatic_mean ~ ICCneg_fz_rev, data= final_data)
SomMod2.2 <- lm(formula = logSomatic_mean ~ ICCneg_fz_rev + RMSDDreact_z, data= final_data)
SomMod2.3 <- lm(formula = logSomatic_mean ~ ICCneg_fz_rev * RMSDDreact_z, data= final_data) 
SomMod2.4 <- lm(formula = logSomatic_mean ~ ICCneg_fz_rev * RMSDDreact_z + FactorScore + Age + Sex + BMI_c + DRMneg_mean_c, data= final_data)

summary(SomMod2.1) #results summaries
summary(SomMod2.2)
summary(SomMod2.3)
summary(SomMod2.4)

apa.reg.table(SomMod2.1, SomMod2.2, SomMod2.3, SomMod2.4)$table_body #model comparison table
```

***you stopped editing here
```{r}
#Positive granularity and corrected HRV reactivity on somatic intensity
SomMod2.1 <- lm(formula = logSomatic_mean ~ ICCneg_fz_rev, data= final_data)
SomMod2.2 <- lm(formula = logSomatic_mean ~ ICCneg_fz_rev + RMSDDreact_z, data= final_data)
SomMod2.3 <- lm(formula = logSomatic_mean ~ ICCneg_fz_rev * RMSDDreact_z, data= final_data) 
SomMod2.4 <- lm(formula = logSomatic_mean ~ ICCneg_fz_rev * RMSDDreact_z + FactorScore + Age + Sex + BMI_c + DRMneg_mean_c, data= final_data)

summary(SomMod2.1) #results summaries
summary(SomMod2.2)
summary(SomMod2.3)
summary(SomMod2.4)

apa.reg.table(SomMod2.1, SomMod2.2, SomMod2.3, SomMod2.4)$table_body #model comparison table
```


### Regressions for Model 2c: Negative granularity and HRV reactivity on self-focused appraisals - SIG FACTOR SCORE

```{r reg-2c}
#Regressions for Model 2c: Negative granularity and corrected HRV reactivity on self-focused appraisals
SelfMod2.1 <- lm(formula = Self ~ ICCneg_fz_rev, data= final_data)
SelfMod2.2 <- lm(formula = Self ~ ICCneg_fz_rev + RMSDDreact_z, data= final_data)
SelfMod2.3 <- lm(formula = Self ~ ICCneg_fz_rev * RMSDDreact_z, data= final_data) 
SelfMod2.4 <- lm(formula = Self ~ ICCneg_fz_rev * RMSDDreact_z + FactorScore + Age + Sex + BMI_c + DRMneg_mean_c, data= final_data)

summary(SelfMod2.1) #results summaries
summary(SelfMod2.2)
summary(SelfMod2.3)
summary(SelfMod2.4)

apa.reg.table(SelfMod2.1, SelfMod2.2, SelfMod2.3, SelfMod2.4)$table_body #model comparison table
```

#### Model Diagnostics

```{r model2c-diagnostic}
model_diagnose_params(SelfMod2.4, 180, final_data)
```

## MODERATIONS: Negative granularity and physio reactivity predicting rating specificity

### Regressions for Model 3a: Negative granularity and SNS reactivity on Neg emo specificity

```{r reg-3a}
#Regressions for Model 3a: Negative granularity and SNS reactivity on Neg emo specificity
SDNegMod3.1 <- lm(formula = SD_NegEmo ~ ICCneg_fz_rev, data= final_data)
SDNegMod3.2 <- lm(formula = SD_NegEmo ~ ICCneg_fz_rev + SNSreact_z, data= final_data)
SDNegMod3.3 <- lm(formula = SD_NegEmo ~ ICCneg_fz_rev * SNSreact_z, data= final_data) 
SDNegMod3.4 <- lm(formula = SD_NegEmo ~ ICCneg_fz_rev * SNSreact_z + FactorScore + Age + Sex + BMI_c + DRMneg_mean_c, data= final_data)

summary(SDNegMod3.1) #results summaries
summary(SDNegMod3.2)
summary(SDNegMod3.3)
summary(SDNegMod3.4)

apa.reg.table(SDNegMod3.1, SDNegMod3.2, SDNegMod3.3, SDNegMod3.4)$table_body #model comparison table
```

#### Model Diagnostics

```{r model3a-diagnostic}
model_diagnose_params(SDNegMod3.4, 180, final_data)
```

### Regressions for Model 3b: Negative granularity and SNS reactivity on somatic specificity

```{r reg-3b}
#Regressions for Model 3b: Negative granularity and SNS reactivity on somatic specificity
SDSomMod3.1 <- lm(formula = SD_SS ~ ICCneg_fz_rev, data= final_data)
SDSomMod3.2 <- lm(formula = SD_SS ~ ICCneg_fz_rev + SNSreact_z, data= final_data)
SDSomMod3.3 <- lm(formula = SD_SS ~ ICCneg_fz_rev * SNSreact_z, data= final_data) 
SDSomMod3.4 <- lm(formula = SD_SS ~ ICCneg_fz_rev * SNSreact_z + FactorScore + Age + Sex + BMI_c + DRMneg_mean_c, data= final_data)

summary(SDSomMod3.1) #results summaries
summary(SDSomMod3.2)
summary(SDSomMod3.3)
summary(SDSomMod3.4)

apa.reg.table(SDSomMod3.1, SDSomMod3.2, SDSomMod3.3, SDSomMod3.4)$table_body #model comparison table
```

#### Model Diagnostics

```{r model3b-diagnostic}
model_diagnose_params(SDSomMod3.4, 180, final_data)
```

### Regressions for Model 3c: Negative granularity and SNS reactivity on appraisal specificity

```{r reg-3c}
#Regressions for Model 3c: Negative granularity and SNS reactivity on appraisal specificity
SDSitMod3.1 <- lm(formula = SD_Sit ~ ICCneg_fz_rev, data= final_data)
SDSitMod3.2 <- lm(formula = SD_Sit ~ ICCneg_fz_rev + SNSreact_z, data= final_data)
SDSitMod3.3 <- lm(formula = SD_Sit ~ ICCneg_fz_rev * SNSreact_z, data= final_data) 
SDSitMod3.4 <- lm(formula = SD_Sit ~ ICCneg_fz_rev * SNSreact_z + FactorScore + Age + Sex + BMI_c + DRMneg_mean_c, data= final_data)

summary(SDSitMod3.1) #results summaries
summary(SDSitMod3.2)
summary(SDSitMod3.3)
summary(SDSitMod3.4)

apa.reg.table(SDSitMod3.1, SDSitMod3.2, SDSitMod3.3, SDSitMod3.4)$table_body #model comparison table
```

#### Model Diagnostics

```{r model3c-diagnostic}
model_diagnose_params(SDSitMod3.4, 180, final_data)
```

### Regressions for Model 4a: Negative granularity and HRV reactivity on Neg emo specificity

```{r reg-4a}
#Regressions for Model 4a: Negative granularity and HRV reactivity on Neg emo specificity
SDNegMod4.1 <- lm(formula = SD_NegEmo ~ ICCneg_fz_rev, data= final_data)
SDNegMod4.2 <- lm(formula = SD_NegEmo ~ ICCneg_fz_rev + RMSDDreact_z, data= final_data)
SDNegMod4.3 <- lm(formula = SD_NegEmo ~ ICCneg_fz_rev * RMSDDreact_z, data= final_data) 
SDNegMod4.4 <- lm(formula = SD_NegEmo ~ ICCneg_fz_rev * RMSDDreact_z + FactorScore + Age + Sex + BMI_c + DRMneg_mean_c, data= final_data)

summary(SDNegMod4.1) #results summaries
summary(SDNegMod4.2)
summary(SDNegMod4.3)
summary(SDNegMod4.4)

apa.reg.table(SDNegMod4.1, SDNegMod4.2, SDNegMod4.3, SDNegMod4.4)$table_body #model comparison table
```

#### Model Diagnostics

```{r model4a-diagnostic}
model_diagnose_params(SDNegMod4.4, 180, final_data)
```

### Regressions for Model 4b: Negative granularity and HRV reactivity on somatic specificity

```{r reg-4b}
#Regressions for Model 4b: Negative granularity and HRV reactivity on somatic specificity
SDSSMod4.1 <- lm(formula = SD_SS ~ ICCneg_fz_rev, data= final_data)
SDSSMod4.2 <- lm(formula = SD_SS ~ ICCneg_fz_rev + RMSDDreact_z, data= final_data)
SDSSMod4.3 <- lm(formula = SD_SS ~ ICCneg_fz_rev * RMSDDreact_z, data= final_data) 
SDSSMod4.4 <- lm(formula = SD_SS ~ ICCneg_fz_rev * RMSDDreact_z + FactorScore + Age + Sex + BMI_c + DRMneg_mean_c, data= final_data)

summary(SDSSMod4.1) #results summaries
summary(SDSSMod4.2)
summary(SDSSMod4.3)
summary(SDSSMod4.4)

apa.reg.table(SDSSMod4.1, SDSSMod4.2, SDSSMod4.3, SDSSMod4.4)$table_body #model comparison table
```

#### Model Diagnostics

```{r model4b-diagnostic}
model_diagnose_params(SDSSMod4.4, 180, final_data)
```

### Regressions for Model 4c: Negative granularity and HRV reactivity on neg appraisal specificity

```{r reg-4c}
#Regressions for Model 4c: Negative granularity and HRV reactivity on  appraisal specificity
SDSitMod4.1 <- lm(formula = SD_Sit ~ ICCneg_fz_rev, data= final_data)
SDSitMod4.2 <- lm(formula = SD_Sit ~ ICCneg_fz_rev + RMSDDreact_z, data= final_data)
SDSitMod4.3 <- lm(formula = SD_Sit ~ ICCneg_fz_rev * RMSDDreact_z, data= final_data) 
SDSitMod4.4 <- lm(formula = SD_Sit ~ ICCneg_fz_rev * RMSDDreact_z + FactorScore + Age + Sex + BMI_c + DRMneg_mean_c, data= final_data)

summary(SDSitMod4.1) #results summaries
summary(SDSitMod4.2)
summary(SDSitMod4.3)
summary(SDSitMod4.4)

apa.reg.table(SDSitMod4.1, SDSitMod4.2, SDSitMod4.3, SDSitMod4.4)$table_body #model comparison table
```

#### Model Diagnostics

```{r model4c-diagnostic}
model_diagnose_params(SDSitMod4.4, 180, final_data)
```


## MODERATIONS: Negative granularity, physio reactivity,and threat v. challenge

```{r reg-5a}
#Regressions for Model 5a: Negative granularity, threat, and SNS on NegHi emotion
TMod5.1 <- lm(formula = NegHiEmo ~ ICCneg_fz_rev, data= final_data)
TMod5.2 <- lm(formula = NegHiEmo ~ ICCneg_fz_rev + Threat_mean_z, data= final_data)
TMod5.3 <- lm(formula = NegHiEmo ~ ICCneg_fz_rev + Threat_mean_z + SNSreact_z, data= final_data)
TMod5.4 <- lm(formula = NegHiEmo ~ ICCneg_fz_rev * Threat_mean_z * SNSreact_z, data= final_data) 
TMod5.5 <- lm(formula = NegHiEmo ~ ICCneg_fz_rev * Threat_mean_z * SNSreact_z + FactorScore + Age + Sex + BMI_c + DRMneg_mean_c, data= final_data)

summary(TMod5.1) #results summaries
summary(TMod5.2)
summary(TMod5.3)
summary(TMod5.4)
summary(TMod5.5)

apa.reg.table(TMod5.1, TMod5.2, TMod5.3, TMod5.4,TMod5.5)$table_body #model comparison table
```


```{r reg-5b}
#Regressions for Model 5b: Negative granularity, challenged, and SNS on NegHi emotion
CMod5.1 <- lm(formula = NegHiEmo ~ ICCneg_fz_rev, data= final_data)
CMod5.2 <- lm(formula = NegHiEmo ~ ICCneg_fz_rev + Challenged_mean_z, data= final_data)
CMod5.3 <- lm(formula = NegHiEmo ~ ICCneg_fz_rev + Challenged_mean_z + SNSreact_z, data= final_data)
CMod5.4 <- lm(formula = NegHiEmo ~ ICCneg_fz_rev * Challenged_mean_z * SNSreact_z, data= final_data) 
CMod5.5 <- lm(formula = NegHiEmo ~ ICCneg_fz_rev * Challenged_mean_z * SNSreact_z + FactorScore + Age + Sex + BMI_c + DRMneg_mean_c, data= final_data)

summary(CMod5.1) #results summaries
summary(CMod5.2)
summary(CMod5.3)
summary(CMod5.4)
summary(CMod5.5)

apa.reg.table(CMod5.1, CMod5.2, CMod5.3, CMod5.4,CMod5.5)$table_body #model comparison table
```

## Plots
```{r reg-plot}
#Plot for Model 1a
NegHiPlot <- ggplot(data=NegHiMod1.4, aes(x=ICCneg_fz_rev, y=NegHiEmo))+
  geom_point(colour= "black", size = 2) + 
  scale_x_continuous(breaks = scales::pretty_breaks(n = 8)) + scale_y_continuous(breaks = scales::pretty_breaks(n = 8))+ 
  geom_smooth(method="lm", colour= "royalblue4", fill="royalblue4") + labs(x="Negative Emotional Granularity", y="Negative High Arousal Emotion Ratings") +  theme(plot.title = element_text(face="bold", hjust = 0.5), axis.title.x = element_text(face="bold"), axis.title.y = element_text(face="bold"), panel.background = element_rect(fill ="white", colour = "black"), axis.ticks.length.y = unit(.1, "cm"),axis.ticks.length.x = unit(-.1, "cm"))
NegHiPlot #printing plot

#Save plot
ggsave("~/Desktop/plot.pdf", plot = last_plot(), device = "pdf", height = 8, width = 8)
```

## MEDIATIONS: Negative granularity and physio reactivity predicting rating intensity

```{r mediate-prep}
mediation_data <- final_data %>%
  dplyr::select(ID, ICCneg_fz_rev, SNSreact, cvRMSDD_TSSTReact, logSomatic_mean, Threat_mean, Challenged_mean, NegHiEmo, SD_NegEmo, SD_SS) %>%
  dplyr::mutate(SNSreact_z = scale(SNSreact, center = F, scale = T),
                RMSDDreact_z = scale(cvRMSDD_TSSTReact, center = F, scale = T),
                Threat_mean_z = scale(Threat_mean, center = F, scale = T),
                Challenged_mean_z = scale(Challenged_mean, center = F, scale = T),)
```
